Deep Learning

### 2015-01-12 deepreview.tex
fixing the wake-sleep, google-cat, and 'more recent' unsupervised citations

Recent work~\citep{Chung-et-al-NIPSDL2014,Yao-et-al-SLU-workshop2014} 
suggests that not all the elements of the LSTM
architecture are required, the crucial element being the presence and learnability 
of the so-called forget gate, controlling the leaking rate (or time constant) of the cell.
%It is not yet clear which aspects of the complicated architecture of LSTMs
%are really necessary. Memory cells are a good way of allowing the
%backpropagated error derivatives to neither explode nor vanish, but they
%are not the only way.  For example, recurrent nets with rectified linear
%hidden units that use the non-linear function $y=max(0,x)$ are much simpler
%than LSTMs and if the recurrent weight matrix is initialized to be close to
%the identity matrix they work about as well as LSTMs both for toy problems
%involving very long-range temporal structure and for real tasks like
%predicting the next word in text\citep{LeHinton}.

@@

This review has focused on supervised learning because of its recent
achievements and we have ignored much interesting work on unsupervised
learning procedures for deep neural 
networks~\citep{Salakhutdinov2009-small,wake-sleep,
  google-cat, denoising-auto, ranzato-pami, more recent}. In the long run,
however, we believe unsupervised learning will be essential for allowing
deep networks to generalize well by creating internal representations that
untangle the many different factors that interact to produce images, speech
and documents~\citep{Yann,Bengio-Courville-Vincent-TPAMI2013}.

>>>>

Recent work~\citep{Chung-et-al-NIPSDL2014-small,Yao-et-al-SLU-workshop2014} 
suggests that not all the elements of the LSTM
architecture are required, the crucial element being the presence and learnability 
of the so-called forget gate, controlling the leaking rate (or time constant) of the cell.
%It is not yet clear which aspects of the complicated architecture of LSTMs
%are really necessary. Memory cells are a good way of allowing the
%backpropagated error derivatives to neither explode nor vanish, but they
%are not the only way.  For example, recurrent nets with rectified linear
%hidden units that use the non-linear function $y=max(0,x)$ are much simpler
%than LSTMs and if the recurrent weight matrix is initialized to be close to
%the identity matrix they work about as well as LSTMs both for toy problems
%involving very long-range temporal structure and for real tasks like
%predicting the next word in text\citep{LeHinton}.

@@

This review has focused on supervised learning because of its recent
achievements and we have ignored much interesting work on unsupervised
learning procedures for deep neural 
networks~\citep{Salakhutdinov2009-small,Hinton95,QuocLe-ICML2012,VincentPLarochelleH2008-small,ranzato-pami,Kingma-et-al-NIPS2014}. 
In the long run,
however, we believe unsupervised learning will be essential for allowing
deep networks to generalize well by creating internal representations that
untangle the many different factors that interact to produce images, speech
and documents~\citep{Yann,Bengio-Courville-Vincent-TPAMI2013}.
